Spanner: Google's Globally-Distributed Database \newline Seminar Report

### 2016-02-16 paper/paper.tex
Iterate Introduction

\section{Introduction \tbr}
\label{sec:introduction}

In the original paper~\cite{Corbett:2012}, Google introduced a
globally-distributed database referred to as \emph{Spanner}. This system is based
upon Paxos~\cite{Lamport:1998} state machines on machines spread across multiple
datacenters across the world. This global replication guarantees high availability
and also implies some desirable locality properties which benefit the performance.

Google already has two other highly scalable distributed databases, i.e.
Bigtable~\cite{Chang:2008} and Megastore~\cite{Baker:2011}. Hence, there must be
a reason, why they did not just use one of these but implemented another
distributed database. According to Google, it is difficult for applications/users
to deal with complex and evolving schemas. Moreover, Bigtable only guarantees to
be eventually-consistent. In contrast, Spanner provides much stronger consistency
guarantees. On the other hand, Megastore suffers from poor write throughput even
though it is used for many applications.

Therefore, Google decided to introduce another distributed, highly available
database system which evolved from a key-value store somehow similar to the one
used by Bigtable (but we will see that this is only partially correct). A core
feature provided by Spanner are so-called \emph{externally-consistent} distributed
general-purpose transactions. Of course, Spanner also provides an SQL-like query
language to enable applications/users to interact with Spanner in a well-known
way. The data is stored in schematized \emph{semi-relational} tables and the data
is versioned automatically. Google also implemented a garbage collection to deal
with old data. The replication can be dynamically configured in order to control
the locality of the replicas. This is useful to control write and read latency
as well as availability. Another main contribution of Spanner are
\emph{globally-consistent} reads at a specific timestamp. This and
externally-consistent reads and writes enable Spanner to provide a special type
of transaction, so-called \emph{schema-change} transactions, which provides atomic
schema changes without locking the whole database and all ongoing transactions.

>>>>

\section{Introduction}
\label{sec:introduction}

In the original paper~\cite{Corbett:2012}, Google introduced a
globally-distributed database referred to as \emph{Spanner}. This system is based
upon Paxos~\cite{Lamport:1998} state machines running on machines spread across
multiple datacenters across the world. This global replication guarantees high
availability and also implies some desirable locality properties which benefit
the performance.

Google already has two other highly scalable distributed databases, i.e.
Bigtable~\cite{Chang:2008} and Megastore~\cite{Baker:2011}. Hence, there must be
a reason, why they did not just use one of these but implemented another
distributed database. According to Google, it is difficult for applications/users
to deal with complex and evolving schemas in Bigtable. Moreover, Bigtable only
guarantees to be eventually-consistent. In contrast, Spanner provides much
stronger consistency guarantees. On the other hand, Megastore suffers from poor
write throughput even though many applications use it.

Therefore, Google decided to introduce another distributed, highly available and
scalable database system which evolved from a key-value store somehow similar to
the one used in Bigtable (but we will see that this is only partially correct).
A core feature provided by Spanner are so-called \emph{externally-consistent}
distributed general-purpose transactions. Of course, Spanner also provides an
SQL-like query language to enable applications/users to interact with Spanner in
a familiar way. The data is stored in schematized \emph{semi-relational} tables
and the data is versioned automatically. Google also implemented a garbage
collection to deal with old data. The replication can be dynamically configured
in order to control the locality of replicas. This is useful to control write
and read latency as well as availability. Another main contribution of Spanner
are high-performance \emph{globally-consistent} reads at a specific timestamp.
This and externally-consistent reads and writes enable Spanner to provide a
special type of transaction, so-called \emph{schema-change} transactions, which
provide atomic schema changes without blocking the whole database.
